Download data

### 2024-05-06 scripts/subsetDataforCrews.Rmd
make fn respect species

lapply(seniors_list[3],  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)
```

>>>>

lapply(seniors_list[3],  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)
